Pulmonary acini exhibit complex changes during postnatal rat lung development

### 2020-12-08 manuscript.tex
Merge branch 'master' of github.com:habi/acinar-analysis-manuscript [ci skip]
This build is based on
https://github.com/habi/acinar-analysis-manuscript/commit/bd33f8a44e5a603397d1f7fc7885ae6b754530aa.

This commit was created by the following CI build and job:
https://github.com/habi/acinar-analysis-manuscript/commit/bd33f8a44e5a603397d1f7fc7885ae6b754530aa/checks
https://github.com/habi/acinar-analysis-manuscript/runs/408035908

This version of the manuscript \href{https://github.com/habi/acinar-analysis-manuscript/compare/d6fc17bd66bdca5cbff30d53e1dbc02d5351609b...eb8aa2674994b5d0a1520095ebc7a0cda2545638}{has been updated} since the first round of review.

This manuscript
(\href{https://habi.github.io/acinar-analysis-manuscript/v/eb8aa2674994b5d0a1520095ebc7a0cda2545638/}{permalink})
was automatically generated
from \href{https://github.com/habi/acinar-analysis-manuscript/tree/eb8aa2674994b5d0a1520095ebc7a0cda2545638}{habi/acinar-analysis-manuscript@eb8aa26}
on December 4, 2020.

@@

\leavevmode\hypertarget{ref-199ALtdJt}{}%
53. Replacement, Reduction, Refinement {[}Online{]}. \emph{ALTEX} 19: 73--78, 2002. \url{https://www.altex.org/index.php/altex/article/view/1106} {[}4 Dec. 2020{]}.
\end{cslreferences}

>>>>

This version of the manuscript \href{https://github.com/habi/acinar-analysis-manuscript/compare/d6fc17bd66bdca5cbff30d53e1dbc02d5351609b...bd33f8a44e5a603397d1f7fc7885ae6b754530aa}{has been updated} since the first round of review.

This manuscript
(\href{https://habi.github.io/acinar-analysis-manuscript/v/bd33f8a44e5a603397d1f7fc7885ae6b754530aa/}{permalink})
was automatically generated
from \href{https://github.com/habi/acinar-analysis-manuscript/tree/bd33f8a44e5a603397d1f7fc7885ae6b754530aa}{habi/acinar-analysis-manuscript@bd33f8a}
on December 8, 2020.

@@

\leavevmode\hypertarget{ref-199ALtdJt}{}%
53. Replacement, Reduction, Refinement {[}Online{]}. \emph{ALTEX} 19: 73--78, 2002. \url{https://www.altex.org/index.php/altex/article/view/1106} {[}8 Dec. 2020{]}.
\end{cslreferences}
